Tables/Graphs for Article

### 2018-01-03 article/draft1.Rnw
edited table 7

% Final model on full data
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{1.5cm} p{4cm}| l | l | l |}
  \hline
 \textbf{Variable} & & \textbf{Hazard Ratio (SE)} & \textbf{95\% CI} & \textbf{p-value}\\ \hline
  \multirow{ 9 }{ 2 cm }{ Device Category } & Apple Product & 0.9346 (0.0476) & & <0.0001 \\ 
  & Camera & -0.3199 (0.0476) & & \\ 
  & Electronics & -0.0138 (0.0904) & & \\ 
  & Game Console & 0.2458 (0.0784) & & \\ 
  & Home & 0.3368 (0.0697) & & \\ 
  & Other & -0.1304 (0.0555) & & \\ 
  & PC & 0.2818 (0.0597) & & \\ 
  & Tablet & -0.1566 (0.0815) & & \\ 
  & Vehicle & 0.4056 (0.0695) & & \\ 
  \hline
  \multicolumn{ 2 }{ |l| }{ Weekend or weekday } & -0.1334 (0.0331) & & <0.0001 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's text contained at least one end punctuation mark } & 0.0247 (0.0499) & & 0.6204 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's text is in all lower case } & -0.1770 (0.0645) & & 0.0061 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among answered questions } & 0.0475 (0.0422) & & 0.2604 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & -0.2808 (0.0340) & & <0.0001 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's title ended in a questionmark } & 0.2571 (0.0332) & & <0.0001 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the user edited or added information to the question's text sometime after posting it } & 0.2983 (0.0857) & & 0.0005 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the user had been a member for less than one day before the question was posted } & -0.1069 (0.0364) & & 0.0033 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & -0.0724 (0.0362) & & 0.0453 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Square root of the average frequency score of a question's tags } & 2.2609 (0.7196) & & 0.0017 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Square root of the average tag length } & -0.0814 (0.0309) & & \\
  & '' & 0.5945 (0.2661) & & \\
  & ''' & -1.5879 (0.7231) & & \\

>>>>

% Final model on full data
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{1.5cm} p{4cm}| l | l | l |}
  \hline
 \textbf{Variable} & & \textbf{Hazard Ratio (SE)} & \textbf{95\% CI} & \textbf{p-value}\\ \hline
  \multirow{ 9 }{ 2 cm }{ Device Category } & Apple Product & 0.9346 (0.0476) & & <0.0001 \\ 
  & Camera & -0.3199 (0.0476) & & \\ 
  & Electronics & -0.0138 (0.0904) & & \\ 
  & Game Console & 0.2458 (0.0784) & & \\ 
  & Home & 0.3368 (0.0697) & & \\ 
  & Other & -0.1304 (0.0555) & & \\ 
  & PC & 0.2818 (0.0597) & & \\ 
  & Tablet & -0.1566 (0.0815) & & \\ 
  & Vehicle & 0.4056 (0.0695) & & \\ 
  \hline
  \multicolumn{ 2 }{ |l| }{ Weekend or weekday } & -0.1334 (0.0331) & & <0.0001 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's text contained at least one end punctuation mark } & 0.0247 (0.0499) & & 0.6204 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's text is in all lower case } & -0.1770 (0.0645) & & 0.0061 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among answered questions } & 0.0475 (0.0422) & & 0.2604 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & -0.2808 (0.0340) & & <0.0001 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the question's title ended in a questionmark } & 0.2571 (0.0332) & & <0.0001 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the user edited or added information to the question's text sometime after posting it } & 0.2983 (0.0857) & & 0.0005 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the user had been a member for less than one day before the question was posted } & -0.1069 (0.0364) & & 0.0033 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & -0.0724 (0.0362) & & 0.0453 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ Square root of the average frequency score of a question's tags } & 2.2609 (0.7196) & & 0.0017 \\ \hline
  \multicolumn{ 2 }{ |p{5.5cm}| }{ \multirow{3}{*}{Square root of the average tag length} } & -0.0814 (0.0309) & & \\
  & & 0.5945 (0.2661) & & \\
  & & -1.5879 (0.7231) & & \\ \hline
